Simple Symmetric Lenses - Foundations and Synthesis

### 2018-05-23 papers/SymmetricLenses/main.tex
add better intro abstract

\begin{abstract}
  Lenses are bidirectional transformers that are often used for synchronizing
  data in different formats. A generalization of lenses, symmetric lenses,
  enable synchronizations between formats where each format contains information
  the other lacks. The theory of symmetric lenses relies heavily on complements
  for maintaining synchronization. Despite the increased expressivity of
  symmetric lenses, no major bidirectional languages or tools have adopted
  symmetric lenses. While the use of complements allows for a clean and general
  formulation of symmetric lenses, it also requires maintaining internal state
  -- in addition to maintaining synchronized files, the complement must also be
  maintained. We simplify the formulation of symmetric lenses to \emph{simple
    symmetric lenses}. These lenses require no complement, instead using
  familiar $create$ and $put$ functions to maintain synchronization.
  Furthermore, we demonstrate the relationship between simple symmetric lenses,
  by carving out a subset of symmetric lenses which are equivalent to simple
  symmetric lenses. We integrate symmetric lenses into a modern bidirectional
  language, Boomerang, while maintaining full backward compatibility.

  Additionally, to enable easy use of symmetric lens combinators, we extend the
  Optician algorithm to synthesize simple symmetric lenses from type and example
  specifications. Unlike the bijective lenses Optician originally addresses,
  there are many symmetric lenses between two data formats. Hypothesizing that
  typically users want the lens that synchronizes the most data, we use an
  information-theoretic measure based on stochastic regular expressions, to
  quantify how much data is left non-synchronized, and develop an algorithm that
  attempts to minimize this measure. Furthermore, as our synthesis algorithm
  requires rewrites to our regular expressions, we prove that these the
  probability distribution of strings within our stochastic regular expressions
  are stable with respect to these rewrites. We experimentally demonstrate that
  despite addressing a much harder problem, our extension to Optician still
  maintains synthesis times competitive to Optician on Optician's bijective
  benchmark suite, and generalizes to benchmarks synchronizing data not in
  bijective correspondence.
\end{abstract}

@@

% begin introduction
\section{Introduction}
% state of the world
Lenses, groups of three functions that satisfy invertibility laws, are useful
formulations for synchronization. Given data in one format, you can view it is a
different data format using \emph{get} function. Given data in another format,
you can turn it into data in the first format using a \emph{create} function.
Given edits on the second format, you can propagate those updates to the first
format using a \emph{put} function. However, writing these three functions is
tedious and error prone. Much better would be to write a single program that
expresses all three of the functions while also guaranteeing invertibility
properties about them.  This is the approach used in many bidirectional
languages: users write code in a bidirectional DSL, and all three functions are
maintained.  These bidirectional languages are often used for data
synchronization tasks - keeping data in different forms synchronized.

While lenses are used to synchronize data formats, but they remain incapable of
synchronizing formats where each format maintains information the other lacks.
To address this, lenses have been generalized to symmetric lenses.  Symmetric
lenses address these synchronization tasks by maintaining an explicit complement
to keep track of projected data.  However, despite the benefits of symmetric
lenses, they have not been adopted into bidirectional languages, remaining instead
as a rarely used Haskell package.

We believe this is largely due to complements. While complements provide a
simple, theoretical framework to express symmetric lenses, they become tricky
when used for synchronization tasks.  Critically, instead of maintaining two
pieces of data (one for each synchronized data format), the lens must now
maintain three (one for each synchronized data format, and one for the
complement).  This can then be difficult when migrating data - I can no longer
copy my formats to a new computer and tell a bidirectional language to keep them
synchronized, I instead must copy my formats and the complement to the new
computer.

We propose an alternative method. Instead of using complements, we can instead
use familiar \emph{create} and \emph{put} methods to synchronize the data
formats. In this paper, we present \emph{simple symmetric lenses}, a
reformulation of symmetric lenses consisting of 4 functions: 2 create functions
and 2 put functions. While these are less expressive than symmetric lenses,
simple symmetric lenses are able to express all synchronization tasks tackled by
asymmetric lenses - all asymmetric lenses are simple symmetric lenses.
Furthermore, we find a predicate over symmetric lenses, where symmetric lenses
satisfy the predicate if, and only if, they can be written as a simple symmetric lens.

As part of our work, we extend Optician to handle symmetric lens combinators,
while maintaining full backwards compatibility. This means simple symmetric
lenses compose simply with both the matching lens and quotient lens combinators
Boomerang provides. Furthermore, despite providing additional capabilities, our
implementation of Boomerang uses fewer lines of code in the core lens library
than were originally present - the symmetry of our lenses enable more code
reuse than the asymmetric versions permitted.

Furthermore, we enable easy use of these combinators by developing a synthesis
algorithm for symmetric lenses within Boomerang. We do this by extending
Optician, a tool for synthesizing bijective lenses, with capabilities for
synthesizing symmetric lenses as well. However, this is not trivial. Bijective
lenses permit relatively few well-typed terms: finding a bijective lens between
two data formats is not easy. However, finding a symmetric lens between two data
formats is relatively easy, as the data synchronization function can be a
``disconnect'' synchronizer -- changing the data in one format doesn't impact
the data in the other. Therefore, we need a means to find the intended symmetric
lens, not merely a symmetric lens. While input-output examples can help, we wish
to make our tool able to synthesize many functions without requiring users to
specify their intent with large example suites.

Instead, we assume that users want to synchronize as much data as possible. To
these ends, we develop an information thereoretic metric measuring the entropy
of how much data is left non-synchronized, utilizing \emph{stochastic regular
  expressions}. We syntactically find the entropy of stochastic regular
expressions for unambiguous stochastic regular expresions. Furthermore, just as
Optician applies rewrites to regular expressions to find well-aligned ones, our
enhancement to Optician applies rewrites to stochastic regular expressions to
find well-aligned ones. We prove these rewrites maintain both the language of
the stochastic regular expressions and the probability distributions over them.

Lastly, we demonstrate the effectiveness of our algorithm by synthesizing all
the bijective transformations present in Optician's benchmark suite with the
new, symmetric algorithm.  Furthermore, we synthesize an additional
\NumBenchmarks new, non-bijective benchmarks.

In summary, our contributions are as follows:
\begin{enumerate}
\item We define simple symmetric lenses and show their relationship with
  symmetric and asymmetric lenses (\S\ref{sec:ssl} and \S\ref{sec:ssl-rels}).
\item We introduce simple symmetric lens combinators that can be used for
  synchronizing string data formats (\S\ref{sec:ssl-string}).
\item We define stochastic regular expressions, demonstrate how to find their
  entropy, and show how certain rewrites on them maintain language and
  probability distribution (\S\ref{sec:stoch-regexp}).
\item We define symmetric DNF lenses, and stochastic DNF regular expressions.
  We show the conversion of regular expression to DNF regular expression
  maintains language and probability distribution.  We show how to infer the
  entropy of a DNF regular expression (\S\ref{sec:dnf-regex-lens}).
\item We describe a synthesis algorithm that attempts to minimize unsynchronized
  information (\S\ref{sec:synthesis}).
\item We provide a fully backwards compatible implementation of symmetric lenses
  in Boomerang, and an implementation of our synthesis algorithm into Optician
  (\S\ref{sec:implementation}).
\item We evaluate our synthesis algorithm on a variety of benchmarks, and find
  that we lose very little synthesis time, while gaining a large amount of
  expressivity (\S\ref{sec:evaluation}).
\end{enumerate}

% end introduction

% begin preliminaries
\section{Preliminaries}
\label{sec:preliminaries}
A \emph{symmetric lens} between $X$ and $Y$ is an element of the type
$\exists C.\{ \mathit{missing} :
C,\,get : X \times C \to Y \times C,\,put : Y \times C \to X \times C\}$
satisfying the following laws:
\begin{equation}
  \tag{\PutRL}
  \frac{\PutR(x,c) = (y,c')}{\PutL(y,c') = (x,c')}
\end{equation}
\begin{equation}
  \tag{\PutLR}
  \frac{\PutL(y,c) = (x,c')}{\PutR(x,c') = (y,c')}
\end{equation}

Two lenses, $\Lens_1$ and $\Lens_2$, are equivalent if
$apply(\Lens_1,\Lens_1.init,es) = apply(\Lens_2,\Lens_2.init,es)$ for all edit
sequences $es$.
% end preliminaries

% begin relationship
\section{Relationships Between Simple Symmetric Lenses and Other Lenses}
\label{sec:ssl-rels}

\begin{theorem}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where
  \begin{enumerate}
  \item $\Lens.creater \App x = \Lens.get \App x$
  \item $\Lens.createl \App y = \Lens.create \App y$
  \item $\Lens.putr \App x \App y = \Lens.get \App x$
  \item $\Lens.putl \App y \App x = \Lens.put \App y \App x$
  \end{enumerate}
\end{theorem}
% end relationship

% begin simple symmetric string lenses
\section{Simple Symmetric String Lenses}
\label{sec:ssl-string}
While we have a theory for simple symmetric lenses, to integrate with Boomerang,
we need combinators to express these lenses. While Boomerang has additional,
complex combinators, we focus on the core ones, which are also those we
eventually wish to synthesize.

% begin stochastic regular expressions
\section{Stochastic Regular Expressions}
\label{sec:stoch-regexp}
To define the entropy for data recovery, we must first develop a probability
model for our languages. We do this by enhancing regular expressions into
\emph{stochastic regular expressions}. With this, we can jointly
express both a language, and a probability distribution over that language.

@@

% end stochastic regular expressions

@@

We have a means of turning stochastic regular expressions into stochastic DNF
regular expressions.
The conversion algorithm itself, written $\ToDNFRegexOf{\Regex}$, is defined below.
\[
  \begin{array}{rcl}
    \ToDNFRegexOf{\String} & = & \DNFOf{\SequenceOf{\String}}\\
    \ToDNFRegexOf{\emptyset} & = & \DNFOf{}\\
    \ToDNFRegexOf{(\PRegexStar{\Regex}{\Probability})} & = & \AtomToDNFOf{\PRegexStar{(\ToDNFRegexOf{\Regex})}{\Probability}}\\
    \ToDNFRegexOf{(\RegexConcat{\Regex_1}{\Regex_2})} & = & \ToDNFRegexOf{\Regex_1} \ConcatDNF \ToDNFRegexOf{\Regex_2}\\
    \ToDNFRegexOf{(\PRegexOr{\Regex_1}{\Regex_2}{\Probability})} & = & \ToDNFRegexOf{\Regex_1} \OrDNF_{\Probability} \ToDNFRegexOf{\Regex_2}\\
  \end{array}
\]
We have also proven an algorithm, demonstrating this conversion respects
probability distributions.

@@

% end DNF regular expressions and lenses

% begin symmetric dnf lenses
\section{Symmetric DNF Lenses}
\label{symmetric-dnf-lenses}
\subsection{Syntax}
Symmetric DNF Lenses are what we synthesize, and we then turn them into
Symmetric Lenses. The nonterminals $i$, $j$, $p$, $q$, $r$, $c$, and $d$ all
represent natural numbers. The nonterminals $\String$ and $\StringAlt$ represent
strings.

@@

\[
  \inferrule*
  {
    \SSQLens_1 \OfType \Sequence_{i_1} \Leftrightarrow \SequenceAlt_{j_1}\\
    \ldots\\
    \SSQLens_p \OfType \Sequence_{i_p} \Leftrightarrow \SequenceAlt_{j_p}\\\\
    i_{c_1} = 1\\
    \ldots\\
    i_{c_q} = q\\\\
    j_{d_1} = 1\\
    \ldots\\
    j_{d_r} = r
  }
  {
    (\SDNFLensOf{(i_1,j_1,\SSQLens_1)\DNFLSep
      \ldots\DNFLSep
      (i_p,j_p,\SSQLens_p)}
    ,\ListOf{c_1;\ldots;c_q}
    ,\ListOf{d_1;\ldots;d_r})
    \OfType\\
    \DNFOf{(\Sequence_1,\Probability_1) \DNFSep \ldots \DNFSep (\Sequence_q,\Probability_q)}
    \Leftrightarrow
    \DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1) \DNFSep \ldots \DNFSep (\SequenceAlt_r,\ProbabilityAlt_q)}
  }
\]

@@

% begin related-work
\section{Related Work}
\label{sec:related}
% end related-work

>>>>

\begin{abstract}
  Similar data is oftentimes represented and stored in different formats. Users
  commonly need to synchronize the data shared between formats, where edits to
  the data in one format gets propagated to the data in the other format.
  Manually writing these data synchronizers is tedious and error prone. To
  alleviate these difficulties, tools have been developed that automatically
  generate these synchronization functions by generating bidirectional lens
  programs from data format descriptors~\cite{optician,quotient-optician}.
  However, these tools only work when the two formats describe exactly the same
  data; it assumes that all important information present in one format is
  present in the other. This is often not the case.

  In this work, we automatically synthesize conversion functions between formats
  that each may contain information the other lacks. We define \emph{simple
    symmetric lenses}, a class of bidirectional programs for expressing these
  types of conversion functions, and we specify a language that expresses simple
  symmetric lenses that operate on string formats. We develop a type-directed
  synthesis algorithm for generating lenses in this language from regular
  expressions describing the data formats. A significant technical challenge in
  this work arises from the fact that our target language permits
  synchronization between formats that don't have exactly the same data -- data
  in one format need not be present in the other format. This gives the
  synthesis algorithm much more freedom, as data can be completely
  unsynchronized (edits in one format are never propagated), completely
  synchronized (the formats are in bijective correspondence), or anywhere in
  between. Under the assumption that users typically want to synchronize as much
  data as possible, we provide an information theoretic metric for how much data
  is left unsynchronized based on the theory of \emph{stochastic regular
    expressions}. Furthermore, we use this metric to develop a greedy synthesis
  algorithm that tries to minimize unsynchronized data. We experimentally
  demonstrate that despite addressing a much harder problem, our extension to
  Optician still maintains synthesis times competitive to Optician on Optician's
  bijective benchmark suite, while generalizing to benchmarks synchronizing data
  not in bijective correspondence.
\end{abstract}

@@

% begin introduction
\section{Introduction}
% state of the world
Similar data can come in varieties of formats: bibliography information can be
stored in the BibTeX, EndNote, or ACM reference formats; web service resources
can be provided to clients in legacy or modern formats; calendar events can be
stored in CSV files or ICS files. Oftentimes, we want to synchronize files
across formats: when my collaborator edits her bibliography stored in the ACM
reference format, I want these edits reflected in my EndNote file; when I update
data through a legacy API, I want those changes to be reflected when I retrieve
it through a modern API; when I create a new calendar event in my ICS file, I
want my CSV calendar files to be updated to reflect this change.

Unfortunately, writing such synchronizers is tedious and error prone.
Bidirectional languages ease the difficulty of writing such synchronizers, as a
single, well-typed program expresses multiple conversion functions, and
guarantee these functions satisfy round-tripping laws. However, bidirectional
languages are difficult to program in as well -- often requiring users to
permute data in fiddly ways while satisfying the type system's complex
unambiguity constraints.

A better approach is to synthesize such conversion functions. Recent research
has gone into automatically synthesizing such conversion functions from
input-output examples and formal descriptions of the data
formats~\cite{optician,quotient-optician}. However, this work assumes that all
data fields present in one format are present in the other, but this is not
always true. Oftentimes, fields present in one format are not present in the
other: updated APIs can expose new information, or omit legacy information; the
ACM reference format includes article number information, whereas EndNote
includes page number information; ICS files contain a URL field that Google
Calendar CSV files do not expose. We aim to synthesize transformations where the
data fields are not necessarily in bijective correspondence, where each data
format can contain important information not present in the other format.

We follow a similar approach to existing work on synthesizing conversion
functions; instead of synthesizing these functions individually, we synthesize
bidirectional programs. To this end, we develop a new formulation of
bidirectional programs, \emph{simple symmetric lenses}, which permit
synchronizations between formats not in bijective correspondence. We develop a
language for expressing simple symmetric lenses that operate on string data.
Terms in this language are typed between regular expressions, where the regular
expressions describe the synchronized data formats.

Our synthesis algorithm takes as input a suite of input-output examples and two
regular expressions describing the data formats. Our synthesis algorithm uses
type-directed synthesis on the two regular expressions to synthesize a lens that
is well-typed between the provided regular expressions and satisfies the
provided input-output examples.

A primary novel difficulty is that, unlike previous work where there are
relatively few well-typed lenses, there are a relatively many well-typed simple
symmetric lenses. As symmetric lenses permit data to be present in only one
format, for any data component there is now a choice: is this data only relevant
to this format and as such should be left unsynchronized, or is this data
present in both formats and as such should be synchronized.

We operate under the assumption that users wish to synchronize as much data as
possible, and try to synchronize as much data as the types and examples allow.
This task gets harder when there are more complex decisions involved. For
example, if I have two fields in one format, and one in the other, which field
on the left should be synchronized to the one of the right? Or would it be
better for the field on the right to be synchronized to a mish-mash of
subcomponents from each field? To answer these questions, we develop a cost
metric for reasoning about which lens synchronizes the most information.

As we wish to synchronize as much data as we can, our cost model gives higher
cost to those with more data is left unsynchronized. In particular, the cost of
a lens is the expected number of bits required to recover a string in one format
when a synchronized string in the other format is provided. In this model,
bijective lenses have zero cost, and as more information is left unsychronized,
the cost is increased.

Our model for this is based on \emph{stochastic regular expressions}~\cite{?}.
We represent a probability distribution for strings by a stochastic regular
expression, and find a way to syntactically infer the expected information
content (or \emph{entropy}) of an unambiguous regular expression. We use this
entropy to calculate the expected information content to recover a string, when
we are given a string it is synchronized to.

We develop an algorithm that synthesizes a low-cost lens. Our algorithm consists
of two communicating synthesizers, one that proposes candidate stochastic
regular expression pairs that it thinks will align well, and one that greedily
searches for a lens between those two regular expressions that minimizes cost
and involves no rewrites.

Our first algorithm, \TypeProp, proposes candidate stochastic regular
expressions. These candidate stochastic regular expressions are generated by
traversing \emph{star semiring} equivalences on stochastic regular expressions.
These proposed stochastic regular expression pairs have equivalent languages and
probability distributions as the original ones: we prove the star-semiring
rewrites this synthesizer applies are sound rewrites on stochastic regular
expression.

Our second algorithm, \GreedySynth, utilizes alternative languages for
stochastic regular expressions and lenses, \emph{stochastic DNF regular
  expressions} and \emph{symmetric DNF lenses}. While these languages are hard
to read and understand, they permit an efficient type-directed synthesis
algorithm. We develop our cost metric on DNF lenses, and provide a greedy
algorithm that tries to find a symmetric DNF lens of minimal cost.

We evaluate our algorithm on a benchmark suite consisting of the original
Optician benchmarks, as well as additional benchmarks consisting of
synchronization tasks where the data is not in bijective correspondence.

In summary, our contributions are:
\begin{enumerate}
\item We develop \emph{simple symmetric lenses} a new formulation for
  bidirectional programs that can project data from both sides~(\S\ref{sec:ssl}),
  and describe a language that expresses such lenses on string
  data~(\S\ref{sec:ssl-string}).
\item We develop a means to traverse stochastic regular expression equivalences,
  while preserving probability distributions and
  languages~(\S\ref{sec:preliminaries}).
\item We develop stochastic DNF regular expressions and DNF lenses. We develop a
  sound algorithm for converting stochastic regular expressions to stochastic
  DNF regular expressions~(\S\ref{sec:dnf-regex-lens}), and a
  information-theoretic cost metric on DNF
  lenses~(\S\ref{sec:symmetric-dnf-lenses}).
\item We extended Boomerang with our simple symmetric lens combinators. We
  updated the Optician synthesis system to synthesize symmetric lenses with our
  new algorithm.
\item We evaluate our synthesis algorithm on Opticians benchmark suite as well
  as new, symmetric benchmarks, and find that we lose very little synthesis
  time, while gaining a large amount of expressivity (\S\ref{sec:evaluation}).
\end{enumerate}
% end introduction

% begin preliminaries
\section{Preliminaries}
\label{sec:preliminaries}
To define the entropy for data recovery, we must first develop a probability
model for our languages. We do this by enhancing regular expressions into
\emph{stochastic regular expressions}. With this, we can jointly
express both a language and a probability distribution over that language.

@@

% end preliminaries

% begin simple symmetric string lenses
\section{Simple Symmetric String Lenses}
\label{sec:ssl-string}
While we have a theory for simple symmetric lenses, to integrate with Boomerang,
we need combinators to express these lenses.

@@

We have a means of turning stochastic regular expressions into stochastic DNF
regular expressions.
The conversion algorithm itself, written $\ToDNFRegexOf{\Regex}$, is defined below.
\[
  \begin{array}{rcl}
    \ToDNFRegexOf{\String} & = & \DNFOf{(\SequenceOf{\String},1)}\\
    \ToDNFRegexOf{\emptyset} & = & \DNFOf{}\\
    \ToDNFRegexOf{(\PRegexStar{\Regex}{\Probability})} & = & \AtomToDNFOf{\PRegexStar{(\ToDNFRegexOf{\Regex})}{\Probability}}\\
    \ToDNFRegexOf{(\RegexConcat{\Regex_1}{\Regex_2})} & = & \ToDNFRegexOf{\Regex_1} \ConcatDNF \ToDNFRegexOf{\Regex_2}\\
    \ToDNFRegexOf{(\PRegexOr{\Regex_1}{\Regex_2}{\Probability})} & = & \ToDNFRegexOf{\Regex_1} \OrDNF_{\Probability} \ToDNFRegexOf{\Regex_2}\\
  \end{array}
\]
We have also proven an algorithm, demonstrating this conversion respects
probability distributions.

@@

This means we also have an algorithm for finding the entropy of an unambiguous
stochastic regular expression, as we can merely convert the regular expression
into DNF form, and find the entropy of it.
% end DNF regular expressions and lenses

% begin symmetric dnf lenses
\section{Symmetric DNF Lenses}
\label{sec:symmetric-dnf-lenses}
\subsection{Syntax}
Symmetric DNF Lenses are what we synthesize, and we then turn them into
Symmetric Lenses. The nonterminals $i$, $j$, $p$, $q$, $r$, $c$, and $d$ all
represent natural numbers. The nonterminals $\String$ and $\StringAlt$ represent
strings.

@@

\[
  \inferrule*
  {
    \SSQLens_1 \OfType \Sequence_{i_1} \Leftrightarrow \SequenceAlt_{j_1}\\
    \ldots\\
    \SSQLens_p \OfType \Sequence_{i_p} \Leftrightarrow \SequenceAlt_{j_p}\\\\
    i_{c_1} = 1\\
    \ldots\\
    i_{c_q} = q\\\\
    j_{d_1} = 1\\
    \ldots\\
    j_{d_r} = r
  }
  {
    (\SDNFLensOf{(i_1,j_1,\SSQLens_1)\DNFLSep
      \ldots\DNFLSep
      (i_p,j_p,\SSQLens_p)}
    ,\ListOf{c_1;\ldots;c_q}
    ,\ListOf{d_1;\ldots;d_r})
    \OfType\\\\
    \DNFOf{(\Sequence_1,\Probability_1) \DNFSep \ldots \DNFSep (\Sequence_q,\Probability_q)}
    \Leftrightarrow
    \DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1) \DNFSep \ldots \DNFSep (\SequenceAlt_r,\ProbabilityAlt_q)}
  }
\]

@@

% begin related-work
\section{Related Work}
\label{sec:related}
A \emph{symmetric lens} between $X$ and $Y$ is an element of the type
$\exists C.\{ \mathit{missing} :
C,\,get : X \times C \to Y \times C,\,put : Y \times C \to X \times C\}$
satisfying the following laws:
\begin{equation}
  \tag{\PutRL}
  \frac{\PutR(x,c) = (y,c')}{\PutL(y,c') = (x,c')}
\end{equation}
\begin{equation}
  \tag{\PutLR}
  \frac{\PutL(y,c) = (x,c')}{\PutR(x,c') = (y,c')}
\end{equation}

Two lenses, $\Lens_1$ and $\Lens_2$, are equivalent if
$apply(\Lens_1,\Lens_1.init,es) = apply(\Lens_2,\Lens_2.init,es)$ for all edit
sequences $es$.

\begin{theorem}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where
  \begin{enumerate}
  \item $\Lens.creater \App x = \Lens.get \App x$
  \item $\Lens.createl \App y = \Lens.create \App y$
  \item $\Lens.putr \App x \App y = \Lens.get \App x$
  \item $\Lens.putl \App y \App x = \Lens.put \App y \App x$
  \end{enumerate}
\end{theorem}

% end related-work
